Summary Tables

### 2020-03-02 summary_tables.Rmd
Create baseline total population distance with suffix for million and billion

>>>>

## Distance tables scaled by using total population (per year in km)
Case study specific distance tables for baseline and five scenarios

```{r trip_tot_dist = "asis", message=F}

bl_td <- list()

require(gt)

for(city in cities){

  print(city)
  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 52, 3)))
  colnames(td)[3:7] <- rownames(scen_prop)

  #

  if (length(bl_td) == 0){
    bl_td <- td %>% dplyr::select(stage_mode)
  }

  td <- td %>% ungroup() %>% janitor::adorn_totals(c('row', 'col'))

  td1 <- td %>% dplyr::select(stage_mode, Baseline)

  names(td1)[2] <- city

  bl_td <- inner_join(bl_td, td1, by = 'stage_mode')

  td1 <- td %>% gt() %>% fmt_number(columns = 2:ncol(td), decimals = T, suffixing = T)

  print(td1)

  # print(kable(td, caption = paste("Distance table (km) for ", city, "( ", sitools::f2si(count_people), " ) per person")))
  cat("\n")

## Baseline total distance tables for all case studies (per year in km)

```{r trip_dist_all_cities = "asis", message=F}

# tab <- bl_td %>% gt() %>% fmt_number(columns = 2:ncol(bl_td), decimals = T, suffixing = T)

# Source: https://stackoverflow.com/questions/28159936/formatting-large-currency-or-dollar-values-to-millions-billions
comprss <- function(tx) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
        c("","K","M","B","T")[div] )
}

backup <- bl_td

td <- as.data.frame(bl_td)

for (i in 2:ncol(td)){
  td[, i] <- comprss(td[, i])

print(kable(td, caption = paste("Distance table (km)")))
